Study of the hadronization of charged pions

### 2017-01-06 1-Answers-Review.tex

{\it Figures \ref{DISKine} illustrates the request and have been added to the note.} \\

\begin{figure}[tbp]
\centering
\includegraphics[width=5cm] {answer-fig/DIS-Q2.png} 
\includegraphics[width=5cm] {answer-fig/DIS-w.png} 
\includegraphics[width=5cm] {answer-fig/DIS-y.png} 
\caption {Inclusive distributions after DIS selection cuts for a sample of the iron
data.}
\label{DISKine}
\end{figure}

11.
P19, eq. 7 - Is it really just the sum of weights or are they the counts multiplied by the 
weights?

{\it They are indeed the counts multiplied by the weights.
The sum indicated runs over all the recorded events, it is not associated to the weight
bins or anything like that. We tried to adapt the language in the note to make it clearer.} \\

@@

12.
P23, I’d be very worried about the MC modeling acceptance on falling edges like that at the 
right of the top right plot.

{\it It is indeed an important issue. A related fact to keep in mind (while it is presented 
later in the note in 2.5.1) is that the main issue there is the quantity of accidentals. Since
the cross section get really small in this region, accidentals start to overcome
the signal. We apply a cut
$p_\perp^2 < 2.5$ GeV$^2$/c$^2$ to remove these regions. One could advocate to even lower this 
cut, but it would affect significantly the outcome of the $\Delta P_\perp^2$, 
because as often with averages the outliers have a strong impact.

On the bright side, the slope and behavior appear to be rather well described by the MC
simulation. We feel that a good reproduction of the data is an indication that the 
acceptance correction will behave properly.} \\

@@

13.
P25, I find this discussion quite confusing.   At top you talk about two binnings.  It’s not just 
binning that is changing, right?  You are using different variables.  Then you talk about the 
extracted weight, but that weight is defined with only one of those sets of variables.  You 
also do it for the other set?  Then you an arbitrary weight cut to take care of the problems 
listed in the middle of the page?  Why not just increase the size of the bins in regions where 
you have too few events or large bin migration?  I don’t see how the procedure you use 
does not lead to holes in your data somehow.  And I don’t really understand what you are 
doing with the second weighting factor.  How is this not doing a double correction for 
acceptance, i.e., a double counting?  This whole section needs to be reworked.  I am fairly 
certain that I don’t really understand what you are doing but it leaves me worried that 
something is amiss.  Anyway, that’s not where you want readers to be.

{ \it The section has been reworked to clarify what we are doing. Few points you raised 
are also answered here:

The first set of variables is the one actually used for the
analysis and the second set is only used to evaluate the systematic errors, so in the 
note, the formulas are given only for the first set.

The motivation for using such a weight cut based on the product of different unrelated
values is actually directly linked to the inbent 
particles being directed in the beam pipe. The $\pi^-$ acceptance drops very 
strongly at low $p_\perp^2$ leading to very high weights, however there is no problem of 
bin migration
or low statistics because the generated yield is very high in this region. We found that 
the best way
to keep these bins while discarding bins where the weight might be slightly smaller but with 
issues concerning bin migration and statistics was to apply this type of cut.

In term of method, the two
step acceptance correction is hopefully going to be clearer. It is the same as the method used 
in the previous L. El Fassi et al. analysis note. The second step of the procedure is
specifically used to take care of the holes in the acceptance (note, they are not really 
holes because problematic bins are generally on the edges). You can see that the weights
of the previously calculated acceptance are used in this step, ensuring that we do not
double correct the data.

The size of the bins is not constant and is indeed increased in region with small event yield.
However, the multi dimensional binning cannot be fully adapted in a general maner. On this
topic we added in annex tables indicating the bin limits that we used.} \\

@@

14.
P26, bottom, if you have regions with very low acceptance, should they be cut out?

{\it In the case of the $\Delta P_\perp^2$, we need to measure an average of the
transverse momentum distribution. Completely cutting a part of the distribution
would indeed solve the acceptance problem but would make the $\langle p_\perp^2 \rangle$
measurement meaning less. We therefore have to live with it and do our best to
reconstruct the whole distribution even if it means having larger error bars.} \\

@@

15.
P26 - "consistent with HERMES results" - could you add HERMES points to the plot with 
your data points to show what you mean as consistent?

{\it To look at } \\

16.
P27 fig.22-
 It's unclear to which point the error bar is associated. I think the common 
practice is to slightly shift markers horizontally.

{\it Sorry, we overlooked this for these intermediary plots. TO BE CORRECTED} \\

@@

17.
P27, Fig. 22 - the right column of plots is not the same as those in Fig. 15.  Why change the 
variables?

{\it Sorry, it is a mistake on our part, there is absolutely no reason. TO BE CORRECTED} \\

@@

20.
P31 - I don’t understand the isospin correction.  It does smooth out the data in Fig. 27; 
however, I am missing the physics motivation.  Why does it matter if the quark came from a 
proton or a neutron?  I think you just clarify the explanation.

21.
P33, Sec. 2.5.1 - list the negligible effects.

22.
P34, Fig. 28 - why is the resolution poorer than in Fig. 12?

{\it Resolution is the same, it looks wider because on this figure, we show the integrated 
result over the 6 sectors. } \\

@@

26.
P35 -
 add plots with systematic uncertainty bands on it to demonstrate bin-by-bin values.

27.
P35, end of top paragraph, you say you don’t include the acceptance systematic, but it looks 
to me like it is included in Table 8?  What am I missing?

28.
P36, top paragraph, “that a factorization holds” means what??  Should explain.

29.
P36 top of section 3.1.1, 5\% versus 5\% looks more like 1 sigma rather than the 1.5 sigma 
you say in the text.

### 2017-01-06 chap5.tex
More questions answered!

However, the implementation of acceptance and radiative corrections is done through some given weights to each event based on its kinematics. The multiplicity ratio then becomes
\begin{equation}
R_A^h (Q^2,\nu,z_h,P_\perp^2) = {{\sum \omega_A^h (Q^2,\nu,z_h,P_\perp^2) / \sum \omega_A^e (Q^2,\nu)} 
                       \over {\sum \omega_D^h (Q^2,\nu,z_h,P_\perp^2) / \sum \omega_D^e (Q^2,\nu)}},
\end{equation}
where $\omega$ is the weight associated with the event, and the sums run over all measured particles. The expression of the transverse momentum broadening remains as
\begin{equation}
\Delta \langle P_\perp^2 \rangle = \langle P_\perp^2 \rangle_A - \langle P_\perp^2 \rangle_D,
\end{equation}
but with
\begin{equation}
\langle P_\perp^2 \rangle = {\sum \left ( P_\perp^2 \times \omega (Q^2,\nu,z_h,P_\perp^2) \right ) \over \sum \omega (Q^2,\nu,z_h,P_\perp^2)}.
\end{equation}

Thus, new expressions of the weighted statistical uncertainties are: 
\begin{equation}
{\delta \left ( R_A^h \right ) \over R_A^h} = 
      \sqrt{ \left ( {\sum {\omega^h_A}^2 \over \left (\sum \omega^h_A \right )^2} \right ) 
           + \left ( {\sum {\omega^e_A}^2 \over \left (\sum \omega^e_A \right )^2} \right ) 
           + \left ( {\sum {\omega^h_D}^2 \over \left (\sum \omega^h_D \right )^2} \right ) 
           + \left ( {\sum {\omega^e_D}^2 \over \left (\sum \omega^e_D \right )^2} \right ) }
\end{equation}
 and 
\begin{equation}
\begin{split}
\left ( \delta \left ( \Delta \langle P_\perp^2 \rangle \right ) \right )^2 = 
   \left ({{\sum \omega^h_A P_\perp^4 }\over{\sum \omega^h_A}} - \left ({\sum \omega^h_A P_\perp^2 }\over{\sum \omega^h_A}\right )^2 \right ) 
         \times \left ( {\sum \left ( {\omega^h_A}^2 \right ) \over \left ( \sum \omega^h_A \right ) ^2 }\right ) \\
 + \left ({{\sum \omega^h_D P_\perp^4 }\over{\sum \omega^h_D}} - \left ({\sum \omega^h_D P_\perp^2 }\over{\sum \omega^h_D}\right )^2 \right ) 
	 \times \left ( {\sum \left ( {\omega^h_D}^2 \right ) \over \left ( \sum \omega^h_D \right ) ^2 }\right ).
\end{split}
\end{equation}

@@

Experimental data were corrected using the weights defined as $\omega = 1/\text{Acc}$. These coefficients are calculated in many bins, in order to be independent of the imperfections of our event generator. However, an excess of bins could lead to a strong bin migration\footnote{Fraction of events not reconstructed in the bin they were produced in.}, which might introduce a bias in case it becomes quite large.

We used a 4-dimensional binning to divide the large phase space of our two particles' final state. However, to evaluate the associated systematic errors with this correction, we used the two different binning presented in table~\ref{tab:AcceptBinning}. The total number of bins is constrained by the amount of generated data, and must be maintained reasonably low in order to keep a good statistical precision and a manageable bin migration.

@@

The weights ($\omega_{\pi^\pm}(\nu,x_{Bj},p_h,t)$) are then extracted from 
the simulation using equation \ref{eq:acc}. However, it turned out that these coefficients should not be applied to data before resolving the issue of the problematic bins that have either
\begin{itemize}
 \item too large weight values, i.e., very small acceptance, or
 \item very few reconstructed events leading to large statistical errors, or
 \item a large fraction of events originally generated in an other bin (bin migration issue).
\end{itemize}
To eliminate these bins we apply the following cuts:
\begin{equation} \label{eq:AccL1}
\left ({\delta \omega \over \omega}\right ) ^2 \times R_c \times \omega < 2,
\end{equation}
and
\begin{equation} \label{eq:AccL2}
N_{rec} > 4,
\end{equation}
where $\delta \omega / \omega$ is the relative error on the weight, and $R_c$ is the 
proportion of reconstructed events initially generated in an other kinematical bin. Figure \ref{fig:AccCoef} shows $\omega$ distributions after applying these cuts. Around 900 bins remain for both targets, but we noticed that these weights are much larger for $\pi^-$ compared to $\pi^+$, as an indication of a larger correction for the inbent particles. In order to maximize the acceptance and reduce the sensitivity to our arbitrary weights' cuts, we corrected the data with an additional two dimensional reweighting factor as:
\begin{equation}
\text{Acc}_2(\nu,p_h) = {\sum_{rec} \omega (\nu,x_{Bj},p_h,t)\over N_{gen}(\nu,p_h)}.
\end{equation}
where $\omega$ is the previously calculated weight of either one remaining bin or a bin that was excluded by the cuts. One of the criteria for setting the limits in equation \ref{eq:AccL1} and 
\ref{eq:AccL2} is to keep reweighting factors, $\omega_2 = 1/\text{Acc}_2$, at the level of a few percents.

>>>>

However, the implementation of acceptance and radiative corrections is done through weights associated to each event based on its kinematics. The multiplicity ratio then becomes
\begin{equation}
R_A^h (Q^2,\nu,z_h,P_\perp^2) = {{\sum \omega_A^h (Q^2,\nu,z_h,P_\perp^2) / \sum \omega_A^e (Q^2,\nu)} 
                       \over {\sum \omega_D^h (Q^2,\nu,z_h,P_\perp^2) / \sum \omega_D^e (Q^2,\nu)}},
\end{equation}
where the sums run over all the events and $\omega$ is the weight associated with the event. The expression of the transverse momentum broadening remains as
\begin{equation}
\Delta \langle P_\perp^2 \rangle = \langle P_\perp^2 \rangle_A - \langle P_\perp^2 \rangle_D,
\end{equation}
but with
\begin{equation}
\langle P_\perp^2 \rangle = {\sum \left ( P_\perp^2 \times \omega (Q^2,\nu,z_h,P_\perp^2) \right ) \over \sum \omega (Q^2,\nu,z_h,P_\perp^2)}.
\end{equation}

Thus, new expressions of the weighted statistical uncertainties are derived: 
\begin{equation}
{\delta \left ( R_A^h \right ) \over R_A^h} = 
      \sqrt{ \left ( {\sum {\omega^h_A}^2 \over \left (\sum \omega^h_A \right )^2} \right ) 
           + \left ( {\sum {\omega^e_A}^2 \over \left (\sum \omega^e_A \right )^2} \right ) 
           + \left ( {\sum {\omega^h_D}^2 \over \left (\sum \omega^h_D \right )^2} \right ) 
           + \left ( {\sum {\omega^e_D}^2 \over \left (\sum \omega^e_D \right )^2} \right ) }
\end{equation}
 and 
\begin{equation}
\begin{split}
\left ( \delta \left ( \Delta \langle P_\perp^2 \rangle \right ) \right )^2 = 
   \left ({{\sum \omega^h_A P_\perp^4 }\over{\sum \omega^h_A}} - \left ({\sum \omega^h_A P_\perp^2 }\over{\sum \omega^h_A}\right )^2 \right ) 
         \times \left ( {\sum \left ( {\omega^h_A}^2 \right ) \over \left ( \sum \omega^h_A \right ) ^2 }\right ) \\
 + \left ({{\sum \omega^h_D P_\perp^4 }\over{\sum \omega^h_D}} - \left ({\sum \omega^h_D P_\perp^2 }\over{\sum \omega^h_D}\right )^2 \right ) 
	 \times \left ( {\sum \left ( {\omega^h_D}^2 \right ) \over \left ( \sum \omega^h_D \right ) ^2 }\right ).
\end{split}
\end{equation}

@@

Experimental data were corrected using the weights defined as $\omega = 1/\text{Acc}$. These 
coefficients are calculated in many bins, in order to be independent of the imperfections of 
our event generator. However, an excess of bins could lead to a large bin 
migration\footnote{Fraction of events not reconstructed in the bin they were produced in.}, 
which introduces a bias in the evaluation of acceptance. Bin sizes are therefore chosen to
be larger than the resolution associated to each kinematic variable.

We used a 4-dimensional binning to divide the large phase space of our two particles' final 
state. To evaluate systematic errors associated with this correction, we compared the
method using two different sets of kinematic variables, as presented in 
table~\ref{tab:AcceptBinning}. The first set of variables is the one actually used for the
analysis and the second set is only used to evaluate the systematic errors, so in the 
following, the formulas are given only for the first set. The total number of bins is 
constrained by the amount of generated data and must be maintained reasonably low in order 
to keep a good statistical precision and a small bin migration.

@@

The weights ($\omega_{\pi^\pm}(\nu,x_{Bj},p_h,t)$) are extracted from 
the simulation using equation \ref{eq:acc}. However, these coefficients should not be applied to data before resolving the issues with bins that have either
\begin{itemize}
 \item too large weight values, i.e., very small acceptance, or
 \item very few reconstructed events and very large statistical errors, or
 \item a large fraction of events originally generated in another bin (bin migration issue).
\end{itemize}
To eliminate these bins we apply the following cuts:
\begin{equation} \label{eq:AccL1}
\left ({\delta \omega \over \omega}\right ) ^2 \times R_c \times \omega < 2,
\end{equation}
and
\begin{equation} \label{eq:AccL2}
N_{rec} > 4,
\end{equation}
where $\delta \omega / \omega$ is the relative error on the weight, and $R_c$ is the 
proportion of reconstructed events initially generated in an other kinematical bin. 
Figure~\ref{fig:AccCoef} shows $\omega$ distributions after applying these cuts. Around 
900 bins remain for both targets, but we noticed that these weights are much larger for 
$\pi^-$ compared to $\pi^+$, as an indication of a larger correction for the inbent 
particles. The motivation for using such a cut based on the product of different unrelated
values is actually directly linked to this problem. The $\pi^-$ acceptance drops very 
strongly at low \pt leading to very high weights, however there is no problem of bin migration
or low statistics because the generated yield is very high in this region. We found that 
the best way
to keep these bins while discarding bins where the weight might be slightly smaller but which 
have issues with bin migration and statistics was to apply this set of cuts.

In order to correct for these droped bins and reduce the sensitivity to the arbitrary in
the choice of the weights' cuts, we corrected the data with an additional two dimensional 
reweighting factor as:
\begin{equation}
\text{Acc}_2(\nu,p_h) = {\sum_{rec} \omega (\nu,x_{Bj},p_h,t)\over N_{gen}(\nu,p_h)}.
\end{equation}
where $\omega$ is the previously calculated weight or a 1 for a bin that was excluded by the 
cuts of equation \ref{eq:AccL1} and \ref{eq:AccL2}. One of the criteria for setting the limits 
in these equation is in fact to keep this reweighting factors, $\omega_2 = 1/\text{Acc}_2$, at 
the level of a few percents. This indicates that the previous method only missed a small 
fraction of the event in the first place and is a good indication of the sanity of the method.
